Reproducibility in plant pathology: where do we stand and a way forward

### 2021-09-01 analysis/paper/paper.Rmd
Rearrange as per CCH suggestion and correct a typo

## Where do we stand in regards to reproducibility?

In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications (see appendix for details on the methodology).

However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).

## Are there good examples in the field?

## Best practices to enhance reproducible research

# Appendix

@@

We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.

@@

>>>>

# Where do we stand in regards to reproducibility?

@@

In an effort to understand where as a discipline we stand as plant pathologists in regards to open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our status.
We randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group-specific publications.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, "Reproducibility_in_plant_pathology_notes.ods", available in this paper's repository in `/inst/extdata'.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.

@@

## Findings

However, data availability was mostly not available with 243 or 81.5% scoring '0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).

# Are there good examples in plant pathology?

# Best practices to enhance reproducible research
